mouse_microbiome

### 2018-07-16 Manuscript_Mouse_Microbiome.Rmd
update

1. Which traits (other than antibiotic resistance) predict OTU tolerance/susceptibility to antibiotics?

@@

#####
#takes too long
#ord <- metaMDS(x_wide, k = 3, trymax = 1000, noshare = 0.2)
#####

myp <- select(x_wide, -Mouse, -Abx, -Dose, -Hour, -Cohoused, -Pair)
myp <- pcoa(vegdist(myp))

j <- data.frame(
  x_wide[, c('Mouse','Abx','Hour','Pair')], 
  PCoA1 = myp$vectors[,1],
  PCoA2 = myp$vectors[,2]) %>%
  group_by(Mouse) %>%
  mutate(
  label = ifelse(Abx == 'Y' & (Hour == min(Hour) | Hour == 120 | Hour == max(Hour)), Hour, NA),
  Abx = factor(ifelse(Abx == 'Y','Abx', 'No abx'), levels = c('No abx', 'Abx')))

@@

@@

iwant <- c('Copies_16S','Forms_biofilms','Gene_number','Obligate_anaerobe','Sporulation')

@@

plot_it(p, name = 'figFiveTraitPatterns', dir = image_dir, width = 6, height = 7.5)

>>>>

1. Which traits (other than antibiotic resistance) predict OTU tolerance/susceptibility to antibiotics?
 + Can they explain differential microbiome community responses to antibiotics?

@@

tmp <- select(x_wide, -Mouse, -Abx, -Dose, -Hour, -Cohoused, -Pair)

#####
#doesn't easily converge... but based on a quick test the results don't differ too much.
ord <- metaMDS(tmp)
ord_scores <- as.data.frame(scores(ord))
#####

myp <- pcoa(vegdist(tmp))
# to see how much of

j <- data.frame(
  x_wide[, c('Mouse','Abx','Hour','Pair')], 
  PCoA1 = myp$vectors[,1],
  PCoA2 = myp$vectors[,2],
  NMDS1 = ord_scores$NMDS1,
  NMDS2 = ord_scores$NMDS2) %>%
  group_by(Mouse) %>%
  mutate(
  label = ifelse(Abx == 'Y' & (Hour == min(Hour) | Hour == 120 | Hour == max(Hour)), Hour, NA),
  Abx = factor(ifelse(Abx == 'Y','Abx', 'No abx'), levels = c('No abx', 'Abx')))

@@

p2 <- j %>% 
  filter(!is.na(Pair)) %>%
  mutate(Pair = paste('Cage', Pair)) %>%
  ggplot(aes(x = NMDS1, y = NMDS2, color = Abx, fill = Abx)) + 
  geom_point(aes(alpha = Hour), shape = 21, size = 4) + 
  geom_point(shape = 21, size = 4, fill = NA) + 
  geom_path() + 
  geom_text(aes(label = label), color = 'black', na.rm=TRUE) +
  scale_color_manual(values = c('black','red')) +
  scale_fill_manual(values = c('black','red')) +
  facet_grid(Pair~Abx) + 
  th

@@

iwant <- c('Obligate_anaerobe','Sporulation')

@@

plot_it(p, name = 'figFiveTraitPatterns', dir = image_dir, width = 6, height = 6)
